---
title: "Analyzing a Cereal Rating Standard"
author: "Chileshe Otieno"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)


library(tidyverse)
library(ggplot2)
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)
library(tm)

Cereal = read.csv('Datasets/cereal.csv',  encoding = "UTF-8")
Cereal = subset(filter(Cereal, type == "C"), select = -c(type, sodium, cups, shelf, potass, mfr, weight, vitamins))
```

[Back to Homepage](https://caseyot6.github.io/)


Data Source: https://www.kaggle.com/crawford/80-cereals

The data is compiled information on nutritional content for various cereals as well as a rating standard
applied to each brand of cereal.

From this data source, cold cereals were selected (cereals requiring no heating to be served).

* Columns/variables selected:
+ Name (Factor), describes name of cereal brand
+ Calories (Integer), describes calories in grams per serving of the cereal
+ Protein (Integer), describes protein in grams per serving of the cereal
+ Fat (Numeric), describes fat in grams per serving of the cereal
+ Carbo (Numeric), describes complex carbohydrates in grams per serving of the cereal
+ Sugars (Integer), describes sugar in grams per serving of the cereal
+ Rating (Numeric), describes rating (0-100) assigned to each brand of cereal





```{r, echo = FALSE}

highest_rating = Cereal %>% arrange(desc(rating)) %>% head(10)

highest_calories =  Cereal %>% arrange(desc(calories)) %>% head(10)

lowest_rating = Cereal %>% arrange(desc(rating)) %>% head(10)

lowest_calories = Cereal %>% arrange(desc(calories)) %>% head(10)

ggplot(data = Cereal) +
  geom_point(aes(x = sugars, y = rating), color = "maroon", size = 3) +
  labs(title = "Rating by Grams of Sugar") +
  xlab("Sugar (grams)") +
  ylab("Rating (0 - 100)")

```

There is a negative relationship between the cereal ratings and grams of sugar present in the cereal.

Based on a linear regression, the relationship is statistically significant at the alpha = .01 level.

R-squared is .5667, indicating that the linear model's relationship between the two accounts for about 56% of the variation in the data.

```{r}
  summary(lm(data = Cereal, rating~sugars))



```


```{r, echo=FALSE}
  
ggplot(data = Cereal) +
  geom_point(aes(x = protein, y = rating), color = "maroon", size = 3) +
  labs(title = "Rating by Grams of Protein") +
  xlab("Proteins (grams)") +
  ylab("Rating (0 - 100)")
```


There seems to be a positive relationship between the cereal ratings and grams of protein present in the cereal.

Based on a linear regression, the relationship is statistically significant at the alpha = .01 level.

R-squared is .2121, indicating that the linear model's relationship between the two accounts for about 21% of the variation in the data.

```{r}
  summary(lm(data = Cereal, rating~protein))
  
```



```{r, echo=FALSE}
  
ggplot(data = Cereal) +
  geom_point(aes(x = fiber, y = rating), color = "maroon", size = 3) +
  labs(title = "Rating by Grams of Fiber") +
  xlab("Fiber (grams)") +
  ylab("Rating (0-100)")
```

There is a positive relationship between the cereal ratings and grams of fiber present in the cereal.

Based on a linear regression, the relationship is statistically significant at the alpha = .01 level.

R-squared is .3879, indicating that the linear model's relationship between the two accounts for about 39% of the variation in the data.

```{r}
  summary(lm(data = Cereal, rating~fiber))
  
```


```{r, echo=FALSE}


ggplot(data = Cereal) +
  geom_point(aes(x = carbo, y = rating), color = "maroon", size = 3) +
  labs(title = "Rating by Grams of Carbohydrate") +
  xlab("Complex Carbohydrates (grams)") +
  ylab("Rating (0-100)")

```

On a glance at the scatterplate, grams of complex carbohydrates and rating do not seem to correlate.

A linear model of the relationship between the two variables shows a p-value greater than an alpha of .05,
indicating a lack of significant relationship between the two.

The linear model appears to only capture 20% of the variation between grams of complex carbs and the rating given to
a cereal brand.

```{r}
  summary(lm(data = Cereal, rating~carbo))
  

```



```{r, echo=FALSE}

highest_rating_cereals = highest_rating %>% left_join(Cereal)
lowest_rating_cereals = lowest_rating %>% left_join(Cereal)


highest_calories_cereals = highest_calories %>% left_join(Cereal)
lowest_calories_cereals = lowest_calories %>% left_join(Cereal)
  
```


## Top 10 Rated Cereals
```{r}

highest_rating_cereals


```


## Bottom 10 Rated Cereals
```{r}

lowest_rating_cereals %>% arrange(desc(rating))


```


## 10 Highest Calorie Cereals
```{r}

highest_calories_cereals


```


## 10 Lowest Calorie Cereals 
```{r}

lowest_calories_cereals %>% arrange(desc(calories))


```




[Back to Homepage](https://caseyot6.github.io/)


